---
title: "Lauren Wolfe's CV"
author: Lauren Wolfe
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume']
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
source("cv_printing_functions.r")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1O0ftne4OJknlrYGyk7JStXRDk6weyLKCf_dvMNnD8BQ/edit?usp=sharing",  
  pdf_mode = params$pdf_mode
)

```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
================================================================================

<!-- ```{r} -->
<!-- # Build interactive network of positions colored by section -->
<!-- # and connected if they occurred in the same year -->
<!-- datadrivencv::build_network_logo(CV$entries_data) -->
<!-- ``` -->


Contact {#contact}
--------------------------------------------------------------------------------

```{r}
CV %>% print_contact_info()
```


Skills {#skills}
--------------------------------------------------------------------------------

- <i class="fa fa-comments-o"></i> **Interpersonal**: _Scientific communication, public speaking, technical writing, meeting facilitation, active listening, adaptability_
<br><br>
- <i class="fa fa-laptop"></i> **Technical**: _GitHub, data analysis, data visualization, reproducibility, open science_
<br><br>
- <i class="fa fa-code"></i> **Programming**: _R, SQL, Python, HTML/CSS, JavaScript_
<br><br>
- <i class="fa fa-rocket"></i> **Other**: _Agile software development, task management software (Trello, Notion, Azure Dev Ops), remote work tools (Slack, MS Teams, Zoom)_


Main
================================================================================

Lauren Wolfe [they/them] {#title}
--------------------------------------------------------------------------------

```{r}
# Note the special double pipe so we modify the CV object in place
CV %<>% print_text_block("intro") 
```

Work Experience {data-icon=laptop}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('work_experience')
```

Volunteering {data-icon=leaf}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('volunteer')
```

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('education')
```

<!-- Publications, Posters, and Talks {data-icon=book} -->
<!-- -------------------------------------------------------------------------------- -->

<!-- ```{r} -->
<!-- CV %<>% print_section('academic_articles') -->
<!-- ``` -->



<!-- ```{r} -->
<!-- CV %<>% print_links() -->
<!-- ``` -->

